Multiset-trie data structure

### 2023-02-24 tex/tex/s_relwork.tex
a lot of changes and added text to responses.
additional comments to reviewers added, and s_relwork.tex changed!

The data structure multiset-trie generalizes the set-trie by providing storage for the set of multisets. When the multiset-trie is restricted to store a set of sets, the underlying data structure becomes a simple binary tree. Moreover, all the operations of the set-trie are also supported by the multiset-trie. The generalization comes with a small penalty in performance if we compare the multiset-trie with the set-trie in the performance of the set containment operations. The downside of such a generalization is that multiset-trie no longer supports path compression that was obtained in set-trie. However, the design of multiset-trie provides storage of multisets with constant worst-case time complexity of the set containment operations.

@@

The index structures for the efficient implementation of the (multi)set containment queries were studied in the frame of the relational DBMS as well as the object-relational DBMS, where we can use multivalued attributes, including sets, multisets (bags), and lists. Zhang et al.\ \cite{Zhang2001} compared the performance of the containment queries implemented in a standard relational DBMS (abbr. RDBMS) to an Information retrieval engine. The results show that, in general, the IR engine performs better than an RDBMS on containment queries. They have identified the problems that reason for the poor performance of the containment operations in an RDBMS and showed that with some modifications, an RDBMS could perform this class of queries more efficiently.

>>>>

The data structure multiset-trie generalizes the set-trie by providing storage for the set of multisets. When the multiset-trie is restricted to store a set of sets, the underlying data structure becomes a simple binary tree. Moreover, all the operations of the set-trie are also supported by the multiset-trie. The generalization comes with a small penalty in performance if we compare the multiset-trie with the set-trie in the performance of the set containment operations. The downside of such a generalization is that multiset-trie no longer supports path compression that was obtained in set-trie. 
%However, the design of multiset-trie provides storage of multisets with constant worst-case time complexity of the set containment operations.

@@

The index structures for the efficient implementation of the (multi)set containment queries were studied in the frame of the relational DBMS as well as the object-relational DBMS, where we can use multivalued attributes, including sets, multisets (bags), and lists. Zhang et al.\ \cite{Zhang2001} compared the performance of the containment queries implemented in a standard relational DBMS (abbr. RDBMS) to an Information retrieval engine. The results show that, in general, the IR engine performs better than an RDBMS on containment queries. The significant causes that differentiate the performance of the IR and RDBMS implementations are the join algorithms employed and the hardware cache utilization. The differences in join algorithms and the cache access method that makes IR queries faster were identified precisely. First, the multi-predicate merge join of the IR engine is different from the standard merge join, and the index nested-loop join algorithms. Second, the study of the utilization of cache in the multi-predicate merge join, standard merge join, and index-nested loop joins has been done, identifying more precisely the differences in the algorithms. They have presented that with some modifications, an RDBMS could perform this class of queries more efficiently.
